\section{Introduction}
\label{sec:introduction}

Synchronous programming languages~\cite{berry92} allow building correct
by construction safety critical hard real-time applications, because
they are based on formal mathematical semantics, which allows the
compiler itself to act as a model-checker~\cite{jagadeesan1995safety}
verifying functional properties of the application. The major benefit of
the synchronous \textit{Model of Computation} (MoC) is that it is based
on the concept of a \textit{Finite State Machine} (FSM). Languages such
as Esterel~\cite{berry92} and its extension SystemJ~\cite{amal10} have
been designed to reduce the state space explosion problem exhibited
during formal verification, by adhering to a very strict programmer
specified state demarcation approach. The programming model for these
languages can be described as follows: a synchronous program is
quiescent until one or more events occur from the environment. Upon
detecting the event, the synchronous program \textit{reacts}
\textit{instantaneously} in zero time to respond to these inputs and
becomes quiescent until the next input events arrive. The start and the
end of this reaction transition demarcate states of the program -- note
that internal data updates do not lead to {\color{red} observable}
change in the program state thereby reducing the state space explosion
problem. Furthermore, the reaction being logically in zero-time is by
definition \textit{atomic} and always faster than the incoming input
events, thereby guaranteeing that none of the incoming events are
missed. In reality, the reaction does take time, one needs to find out
the \textit{Worst Case Reaction Time} (WCRT) of any given synchronous
program. This WCRT value determines the shortest inter-arrival time for
input events from the environment. {\color{black} The requirement that
  all input events from the environment arrive at beast WCRT time units
  apart, guarantee that no input event goes unhandled and hence,
  enforces the \textit{zero} delay synchronous hypothesis.}

Techniques exist for computing WCRT values for synchronous programs
providing support for data-computation via a non-managed language
(primarily `C')~\cite{boldt07} and~\cite{proop10}. These WCRT estimation
approaches suffer from a fundamental problem; they cannot incorporate
complex data-computations within the WCRT analysis framework, because of
the many undefined behaviors, type unsafety and the general lack of
formal operational semantics inherent to low-level non-managed
languages. Hence, in this paper we are interested in the WCRT analysis
of programs that support data computation via managed-languages like
Java, which provides a well defined operational
semantics. {\color{black} SystemJ is the only programming language based
  on the GALS MoC that uses Java for its data computations.} The key
hurdle to the adoption of managed languages in the safety critical hard
real-time application domain is \textit{Garbage Collection} (GC) for
automatic memory management, since worst case execution time estimates
for GC cycles are very pessimistic~\cite{puffitsch2013design}.

{\color{black}

  We identify the following requirements for WCRT analysis of SystemJ
  programs with automated memory management:

  \begin{enumerate}

  \item The number and clock-cycles of instructions used for memory
    allocation and reclaim should be statically bounded (to a constant
    value) at compile time. This is necessary, because the primary
    problem with long garbage collection times is the fact that garbage
    collection time depends upon the size of physical memory and the
    number of object allocated during program
    execution~\cite{schoeberl2010scheduling}.

  \item The size of each object and consequently the total memory
    consumption should be bounded (to a constant value) statically at
    compile time. JVM specification requires resetting all the memory
    (filling it with zeros) allocated for each object. Adhering to the
    first point requires that the size of the object be known
    statically, so that the loop zeroing the memory of the allocated
    object can be bounded. If all the object sizes can be determined
    statically, then the physical memory size can also be bounded.

  \end{enumerate}

}

% On the one hand GC guarantees no memory leaks, thereby providing
% functional safety, but on the other hand, it has been
% shown~\cite{puffitsch2013design} that using even a state of the art
% real-time GC results in very pessimistic worst case execution time
% estimates for real-time tasks.,~\footnote{The worst case execution time
%   was estimated to be in seconds due to the GC, but the observed time
%   was in milli-seconds.} compared to the observed task execution times,
% thereby rendering worst case execution/reaction time analysis unfeasible
% in the general case with a GC.

The main \textbf{contribution} presented in this paper is a new memory
management approach that is amenable, to static WCRT analysis by
satisfying the aforementioned requirements. More concretely our
contributions are as follows:

\begin{itemize}
\item \textit{Programming model inspired memory organization}: In this
  paper we present a new memory organization for Java and an
  accompanying static WCRT analysis based on SystemJ's MoC.
\item \textit{Compiler supported memory allocation}: We present the
  compiler transformations that are needed to statically guarantee the
  \textit{Worst Case Memory Consumption} (WCMC) and \textit{allocation}.
\item \textit{Time analyzable back-end code generation and garbage
    collection}: We present a strategy to replace the object allocation
  bytecodes with real-time analyzable alternatives. Furthermore, we also
  present an object placement strategy, which allows for O(1) heap
  accesses in all cases.
\end{itemize}

% We use the SystemJ~\cite{amal10} programming language, because it
% provides the synchronous MoC as a subset along with Java data-driven
% computation support. Furthermore, there exist efficient and real-time
% analyzable execution architectures~\cite{nadeem2011rjop} and WCRT
% analysis tools~\cite{LiMS14} that support subset of SystemJ programs --
% those without GC invocation.




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "rts"
%%% End:
